Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-14 draftfinalreport_v4.Rnw
adds 'on top of current childhood vaccination rates' to summary of additional vacciation required

\item Of the \Sexpr{naive_percent}\% of the overall population of New Zealand that are currently considered to be immunologically na\"{\i}ve to measles, it was estimated that approximately \Sexpr{vacc_reqd_percent}\% of those would require additional vaccination to ensure measles does not persist and outbreaks do not occur, leading to an additional \Sexpr{vacc_reqd_count} effective vaccinations nationally.

>>>>

\item Of the \Sexpr{naive_percent}\% of the overall population of New Zealand that are currently considered to be immunologically na\"{\i}ve to measles, it was estimated that approximately \Sexpr{vacc_reqd_percent}\% of those would require additional vaccination on top of current childhood vaccination rates to ensure measles does not persist and outbreaks do not occur, leading to an additional \Sexpr{vacc_reqd_count} effective vaccinations nationally.
